# About the Author {-}

Frida Gomam is a famous lady. Police will always let her go.
\mainmatter

# Introduction

Now unplug your Internet cable, and start doing some serious work.

We have a nice figure in Figure \@ref(fig:hello), and also a table in Table \@ref(tab:iris).

```{r hello, fig.cap='A figure.'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19)
```

```{r iris}
knitr::kable(
  head(iris), caption = 'The boring iris data.',
  booktabs = TRUE
)
```

More chapters to come in `02-foo.Rmd`, `03-bar`.Rmd, ...
# The FOO Method

We talk about the _FOO_ method\index{FOO} in this chapter.

\cleardoublepage 

# (APPENDIX) Appendix {-}

# More to Say

Yeah! I have finished my book, but I have more to say about some topics. Let me explain them in this appendix.

To know more about **bookdown**, see https://bookdown.org.
`r if (knitr:::is_html_output()) '# References {-}'`

```{r include=FALSE}
# generate a BibTeX database automatically for some R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

